---
title: "Data report"
author: "Angelina Venetto"
date: "3/31/2022"
output: html_document
---

```{r setup, include=FALSE}
install.packages("tidytuesdayR")\
(library)tidyverse::
```
```{r setup, include=FALSE}
library(tidytuesdayR)
library(tidyverse)
library(ggrepel)    
library(ggtext)
```

```{r}
chocolate <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-18/chocolate.csv')
```
#This project aims to examine which country manufactured the highest rated chocolate in 2021

#Data was found here: https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-18/readme.md

```{r}
ggplot(chocolate) +
  aes(x = country_of_bean_origin,
      y = rating,
      fill = rating,
      color = rating) +
  geom_point() 
```
#Filtering data from the last 5 years, while dropping any data with out a rating. Also grouping by country
```{r}
chocolate_clean <- chocolate %>%
  select(year = review_date, country = company_location, rating = rating)
```
```{r}
rating <- "rating"
country <- "country"
year <- "year"

```
#clean the data by filtering the year 2021, droping all NA from year and country, sumamrzing the ratings as thr mean rating per country for that year,selecting only country, year, and rating columns
```{r}
chocolate_rates <- chocolate_clean %>% 
 filter(year %in% c(2021)) %>% 
  drop_na(country, rating) %>%
 group_by(country)%>%   
summarize(rating = mean(rating))
ungroup() %>%  
  select(country, year, rating) %>% 


  #making the data set wider
pivot_wider(
   id_cols = country,
   names_from = (year), 
   values_from = rating,
   ) 
 
chocolate_rates
```
#Making a plot for data vizualisation 
```{r}
update_geom_defaults("text", list(family = "FiraGO"))
update_geom_defaults("label", list(family = "FiraGO"))
update_geom_defaults("label_repel", list(family = "FiraGO"))

ggplot(chocolate_rates) +
  aes( x = rating,
    y = country, 
      color = country,
      fill= country
   ) +
  geom_point() 
```
#overall, based on the plot, the country with the highest ranked chocolate in the year 2021 was France. Scotland had the lowest ranked chocolate. 
