---
title: "Data report"
author: "Angelina Venetto"
date: "3/31/2022"
output: html_document
---


```{r setup, include=FALSE}
library(tidytuesdayR)
library(tidyverse)
library(ggrepel)    
library(ggtext)
```

```{r}
chocolate <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-18/chocolate.csv')
```
#This project aims to examine which country manufactured the highest rated chocolate in 2021

#Data was found here: https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-18/readme.md


#renaming some variables
```{r}
chocolate_clean <- chocolate %>%
  select(year = review_date, country = company_location, rating = rating)
```
#creating objects with variables in use
```{r}
rating <- "rating"
country <- "country"
year <- "year"

```
#clean the data by filtering the year 2021, droping all NA from year and country, sumamrzing the ratings as their mean rating per country for that year,selecting only country, year, and rating columns
```{r}
chocolate_rates <- chocolate_clean %>% 
 filter(year %in% c(2021)) %>% 
  drop_na(country, rating) %>%
 group_by(country)%>%   
summarize(rating = mean(rating))

 
chocolate_rates
```
#Making a plot for data vizualisation 
```{r}
update_geom_defaults("text", list(family = "FiraGO"))
update_geom_defaults("label", list(family = "FiraGO"))
update_geom_defaults("label_repel", list(family = "FiraGO"))
ggplot(chocolate_rates) +
  aes( x = rating,
    y = country, 
      color = country,
      fill= country
   ) +
  geom_point() 
```

#overall, based on the plot, the country with the highest ranked chocolate in the year 2021 was France. Scotland had the lowest ranked chocolate. 
